Legends for Figures

### 2019-05-08 Manuscript/Figures/figure_legends.Rmd
cleaning up legends
editted figure legends

**Figure 4. Resolution-specific data summaries.** (A) The total number of genomic bins created by partitioning the linear genome into unit intervals corresponding to the resolution of the relevant domain data for the GM12878 (red) and K562 (blue) cell line. (B) Subsequent imbalance ratios created when labelling bin class, defined as the ratio of the number of bins that overlapped with a flanked TAD boundary to the number of bins that did not overlap with a flanked TAD boundary.

@@

**Figure 7. Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 10 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D). For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary. That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.

>>>>

**Imbalance Ratios.** Boxplots illustrating the variations in imbalance ratios (IR) across cell line and resolution. IR was calculated by dividing the number of chromosome-specific genomic bins that overlapped with flanked TAD boundaries by the number of chromosome-specific genomic bins that did not.

@@

<!--
**Figure 7. Comparing $log_{2}$ distance profiles of top predictive transcription factor binding sites by bin class for 10 kb resolution, on GM12878.** Violin plots (top) and plots of differences in quantiles (bottom) between genomic bin class for 4 of the top predictive TFBS determined by the best performing model, including: SMC3 (A), ZNF143 (B), CTCF (C), and RAD21 (D). For the plots of differences in quantiles, the reference group are the genomic bins that did not overlap with a flanked TAD boundary. That is, quantile differences above 0 indicate that bins that overlapped with flanked TAD boundaries exhibited smaller quantiles.
-->
